Automatic Matching of Bullet Lands

### 2016-01-04 imaging-paper.Rnw
random thing from git

Figure~\ref{fig:varysmooth} displays the  peaks and valleys detected in the same signature at smoothing factors of 5, 25, and 45, respectively. The dark line corresponds to the smoothed values, while the grey line in the back shows the raw signature. The choice of smoothing factor is a classical decision of a bias/variance trade-off. It is immediately clear that a small smoothing factor like 5 is a poor choice. It results in a significant amount of noise in the data such that even just a point or two can skew the rolling average enough for a peak or valley to be detected. Given that the striation patterns are typically much larger, we are in effect muddying the waters by performing such minimal smoothing. Another consideration is that the smoothing should not fall below the  resolution of the equipment at which the surface measurements are taken -- in order to not introduce artefacts in the analysis.

>>>>

Figure~\ref{fig:varysmooth} displays the  peaks and valleys detected in the same signature at smoothing factors of 5, 25, and 45, respectively. The dark line corresponds to the smoothed values, while the grey line in the back shows the raw signature. The choice of smoothing factor is a classical decision of a bias/variance trade-off. It is immediately clear that a small smoothing factor like 5 is a poor choice. It results in a significant amount of noise in the data such that even just a point or two can skew the rolling average enough for a peak or valley to be detected. Given that the striation patterns are typically much larger, we are in effect muddying the waters by performing such minimal smoothing. Another consideration is that the smoothing should not fall below the  resolution of the equipment at which the surface measurements are taken -- in order to not introduce artifacts in the analysis.
